### 2018-03-14 Physics Notes/Nuclear Physics/Nuclear Energy/Nuclear Energy.tex
Notes update

>>>>

\subsubsection{Example}
\textit{How much energy would be produced by the fission of 10kg of $^{235}_{92}U$}
$$^{235}_{92}U+^1_0n\rightarrow ^{141}_{56}Br+^{92}_{36}Kr+3 \ ^1_0n$$
$$235.04393u+1.00867u\rightarrow140.9408u+91.9298u+\times1.00867u$$
$$\textrm{Difference}=0.15599u=145.3MeV$$
Find the total number of atoms
$$\textrm{Number of atoms}=\frac{\textrm{Mass}}{\textrm{Nucleon Number}}\times \textrm{Avagadro's constant}$$
$$\textrm{Number of atoms}=\frac{10}{235.04393\times10^{-3}}\times6.02\times10^{23}=2.56\times10^{25}$$
Multiply the energy released per atom by the number of atoms to find the total energy released
$$\textrm{Total energy}=2.56\times10^{25}\times145.3=3.72\times10^{27}MeV$$
